CMPSubset

### 2021-08-13 CMP/CMPSubset.Rmd
is this cleaning or breaking
more reorganizing

## Update 2021.08.11
Most thorough way to readdress differences between original and current analyses is to jsut redo the biomark. To that end, will restart analysis of *just* CMPm2, excluding other datasets (i.e., LSK, MEP, GMP). Will also keep CMP3K as test set/ bio rep 1

@@

```{r setup}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/")
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
# library(clustree)
```

@@

store session info
```{r }
sessionInfo.filename <- paste0(projectName, "_sessionInfo.txt")
sink(sessionInfo.filename)
sessionInfo()
sink()
```

>>>>

## Update 2021.08.11
Most thorough way to readdress differences between original and current analyses is to jsut redo the biomark. To that end, will restart analysis of *just* CMPm2, excluding other datasets (i.e., LSK, MEP, GMP). Will also keep

@@

```{r setup}
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
# library(clustree)
```

@@

store session info
```{r }
# sink("CMP-v1.20210616.txt")
sessionInfo()
# sink()
```
